Lattice Boltzmann study of mass transfer for complicated geometries

### 2012-02-01 Text/introduction.tex
Worked with text.

@@

@@

@@

boundary conditions. Thus, let us introduce the new variable, $\Theta=C-C_{wall}$, which makes the system to be with homogenous boundary conditions:

@@

@@

\subsection{The parabolic profile mass transfer and comparison}
The problem we want to address can be formulated through the following PDE:

@@

the following can be obtained:

>>>>

&C(0,y)=C_0,\, C(x,0)=\cstar,\, \frac{\partial C}{\partial y }(x,\delta)=0\\

@@

&C(0,y)=C_0,\, C(x,0)=\cstart,\, \frac{\partial C}{\partial y }(x,H)=0\\

@@

&C(\zeta,0)=\cstar\\

@@

boundary conditions. Thus, let us introduce the new variable, $\Theta=C-\cstar$, which makes the system to be with homogenous boundary conditions:

@@

&\Theta(0,\xi)=C_0-\cstar \\

@@

\subsection{The Poiseuille parabolic profile}
The problem can be formulated through the following PDE:

@@

the following equation can be obtained:
